\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 stlc-linkTran-typing.tex
Fix typo in LT example.

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\begin{tabular}{|l|l|l|l|}
\hline
\rowcolor[HTML]{FFFFE6} 
surface-syntax program & $i$ & $\sigma_i = \LSigAdd{\sigma_{i-1}}{s_i}{T_i}$ & $\sigma_i' = \LSigAdd{\sigma_{i-1}'}{s_i'}{T_i'}$ \\ \hline
\lsti!Family STLC_bool...! & 0        & $\{\}$                                   & $\{\}$                                   \\ \cline{2-4} 
\lsti!FInductive tm +=!     & 1        & $\{"tm" : \TyS{\wcode{\wsig_1}}\}$       & $\{"tm" : \TyS{\wcode{\wsig_1'}}\}$      \\ \cline{2-4} 
\lsti!| .. | tm_true | ..!  & 2        &                                          &                                          \\
                      &          &                                          &                                          \\ \cline{2-4} 
\lsti!FRecursion subst!     &          &                                          &                                          \\ \cline{2-4} 
\rowcolor[HTML]{E0D7D7} 
\lsti!(* Inherit ... *)!    & $\alpha$ & $\RecSig{\wsig_1}{"tm"}$                 & $\RecSig{\wsig_1}{"tm"}$                 \\ \cline{2-4} 
\rowcolor[HTML]{E0D7D7} 
\lsti!Case tm_true ...!        & $\beta$  & $\sigma_{\alpha}$                        & $\{.. "tm:true": \}$                     \\ \cline{2-4} 
\lsti!End subst!            & 3        & $\{.. "subst'" : \TyLkg{\lsig_\alpha}\}$   & $\{.. "subst"' : \TyLkg{\lsig_\beta'}\}$   \\ \cline{2-4} 
                      & 4        & $\{.. "subst" : \El{"tm"} \to id \to ..\}$ & $\{.. "subst" : \El{"tm"} \to id \to ..\}$ \\ \cline{2-4} 
\lsti!(* Inherit t1 *)!     & 5        & $\{.. "t"_1 : \El{"tm"}\}$               & $\{.. "t"_1 : \El{"tm"}\}$               \\
                      &          &                                          &                                          \\ \hline
\end{tabular}
\end{centered}

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFFE6} 
surface-syntax program     & $i$      & $\goodInh{..}{h_i}{\sigma_i}{\sigma_i'}$             \\ \hline
\lsti!Family STLC_bool...! & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm +=!     & 1        & $\InhOv{h_0}{\wcode{\wsig_1'}}$                      \\ \cline{2-3} 
\lsti!| .. | tm_true | ..!  & 2        &                                                      \\
                        &          &                                                      \\ \cline{2-3} 
\lsti!FRecursion subst!     &          &                                                      \\ \cline{2-3} 
\rowcolor[HTML]{E0D7D7} 
\lsti!(* Inherit ... *)!    & $\alpha$ & $\InhId$                                             \\ \cline{2-3} 
\rowcolor[HTML]{E0D7D7} 
\lsti!Case tm_true ...!        & $\beta$  & $\InhExt{h_\alpha}{..}$                              \\ \cline{2-3} 
\lsti!End subst!            & 3        & $\InhNest{h_1}{h_\beta}$ with $\uparrow s_3$         \\ \cline{2-3} 
                        & 4        & $\InhOv{h_3}{\lambda t. \Wrec{\wsig_1'}{t}{"subst'"}}$ \\ \cline{2-3} 
\lsti!(* Inherit t1 *)!     & 5        & $\InhInh{h_4}$ with $\uparrow s_4$                   \\
                        &          &                                                      \\ \hline
\end{tabular}
\end{centered}

@@

When sketching signature $\lsig$, we use curly bracket as a shorthand for signature and square bracket as a shorthand for (deeply) nested sigma type (usually used in the case of $\TyTkg{\cdot}$). Because every $\lsig_i$ is always constructed from $\lsig_{i-1}$ so in the figure we omit the previous fields in each signature.  The only exceptions are the rows indexed by $\alpha$ and $\beta$. These two rows are describing a nested family for case handlers, and $\lsig_\beta$ is constructed by $\lsig_\alpha$.

@@

Note that in our table, the Row 2 only has information of $A_2$ and $A_2'$ (i.e. there is no $\lsig_2$ and $\lsig_2'$). We especially use one row to indicate that $s_2$ and $s_2'$ is ``sealing/abstracting'' $\lsig_1' = \{"tm" : \TyS{\wcode{\wsig_1'}}\}$, into a nested dependent pair of "tm" type and its constructors $A_2' = ["tm" : \cU, "tm_var" : id \to \El{"tm"}, "tm_lam" : id \to \El{"tm"} \to \El{"tm"}, "tm_app" : \El{"tm"} \to \El{"tm"} \to \El{"tm"}]$.

>>>>

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\begin{tabular}{|l|l|l|l|}
\hline
\rowcolor[HTML]{FFFFE6} 
surface-syntax program & $i$ & $\lsig_i = \LSigAdd{\lsig_{i-1}}{s_i}{T_i}$ & $\lsig_i' = \LSigAdd{\lsig_{i-1}'}{s_i'}{T_i'}$ \\ \hline
\lsti!Family STLC_bool...! & 0        & $\{\}$                                   & $\{\}$                                   \\ \cline{2-4} 
\lsti!FInductive tm +=!     & 1        & $\{"tm" : \TyS{\wcode{\wsig_1}}\}$       & $\{"tm" : \TyS{\wcode{\wsig_1'}}\}$      \\ \cline{2-4} 
\lsti!| .. | tm_true | ..!  & 2        & N/A                                         & N/A                                         \\
                      &          &                                          &                                          \\ \cline{2-4} 
\lsti!FRecursion subst!     &          &                                          &                                          \\ \cline{2-4} 
\rowcolor[HTML]{E0D7D7} 
\lsti!(* Inherit ... *)!    & $\alpha$ & $\RecSig{\wsig_1}{"tm"}$                 & $\RecSig{\wsig_1}{"tm"}$                 \\ \cline{2-4} 
\rowcolor[HTML]{E0D7D7} 
\lsti!Case tm_true ...!        & $\beta$  & $\lsig_{\alpha}$                        & $\{.. "tm:true": \}$                     \\ \cline{2-4} 
\lsti!End subst!            & 3        & $\{.. "subst'" : \TyLkg{\lsig_\alpha}\}$   & $\{.. "subst"' : \TyLkg{\lsig_\beta'}\}$   \\ \cline{2-4} 
                      & 4        & $\{.. "subst" : \El{"tm"} \to id \to ..\}$ & $\{.. "subst" : \El{"tm"} \to id \to ..\}$ \\ \cline{2-4} 
\lsti!(* Inherit t1 *)!     & 5        & $\{.. "t"_1 : \El{"tm"}\}$               & $\{.. "t"_1 : \El{"tm"}\}$               \\
                      &          &                                          &                                          \\ \hline
\end{tabular}
\end{centered}

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFFE6} 
surface-syntax program     & $i$      & $\goodInh{..}{h_i}{\lsig_i}{\lsig_i'}$             \\ \hline
\lsti!Family STLC_bool...! & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm +=!     & 1        & $\InhOv{h_0}{\wcode{\wsig_1'}}$                      \\ \cline{2-3} 
\lsti!| .. | tm_true | ..!  & 2        & N/A                                                     \\
                        &          &                                                      \\ \cline{2-3} 
\lsti!FRecursion subst!     &          &                                                      \\ \cline{2-3} 
\rowcolor[HTML]{E0D7D7} 
\lsti!(* Inherit ... *)!    & $\alpha$ & $\InhId$                                             \\ \cline{2-3} 
\rowcolor[HTML]{E0D7D7} 
\lsti!Case tm_true ...!        & $\beta$  & $\InhExt{h_\alpha}{..}$                              \\ \cline{2-3} 
\lsti!End subst!            & 3        & $\InhNest{h_1}{h_\beta}$ with $\uparrow s_3$         \\ \cline{2-3} 
                        & 4        & $\InhOv{h_3}{\lambda t. \Wrec{\wsig_1'}{t}{"subst'"}}$ \\ \cline{2-3} 
\lsti!(* Inherit t1 *)!     & 5        & $\InhInh{h_4}$ with $\uparrow s_4$                   \\
                        &          &                                                      \\ \hline
\end{tabular}
\end{centered}

@@

When sketching signature $\lsig$, we use curly bracket as a shorthand for signature and square bracket as a shorthand for (deeply) nested sigma type (usually used in the case of $\TyTkg{\cdot}$). Because every $\lsig_i$ is always constructed from $\lsig_{i-1}$ so in the figure we omit the previous fields in each signature.  One exception are the rows indexed by $\alpha$ and $\beta$. These two rows are describing a nested family for case handlers, and $\lsig_\beta$ is based on $\lsig_\alpha$. The other exception is $\lsig_3$. $\lsig_3$ is based on $\lsig_1$.

@@

Note that in our table, the Row 2 only has information of $A_2$ and $A_2'$ (i.e. there is no $\lsig_2$ or $\lsig_2'$). We especially use one row to indicate that $s_2$ and $s_2'$ is ``sealing/abstracting'' $\lsig_1' = \{"tm" : \TyS{\wcode{\wsig_1'}}\}$, into a nested dependent pair of "tm" type and its constructors $A_2' = ["tm" : \cU, "tm_var" : id \to \El{"tm"}, "tm_lam" : id \to \El{"tm"} \to \El{"tm"}, "tm_app" : \El{"tm"} \to \El{"tm"} \to \El{"tm"}, "tm_true" : \El{"tm"}, "tm_false" : \El{"tm"}]$.
